cardinalR: Generating interesting high-dimensional data structures

### 2025-09-08 paper-cardinalR.Rmd
Changes up to pyramid types

The Mobius strip is generated using `geozoo::mobius(n, p = 3)$points`, which samples $n$ points from a parametrization of the surface defined by angle $\theta$ and strip width $w$. The cartesian coordinates are $X_1 = \left(1 + w/2 \cos(\theta/2)\right) \cos(\theta)$, $X_2 = \left(1 + w/2 \cos(\theta/2)\right) \sin(\theta)$, and $X_3 = w/2 \sin(\theta/2)$. This maps a $2\text{-}D$ band with a half-twist into $3\text{-}D$ space, forming a non-orientable one-sided surface. For $p > 3$, Gaussian noise $X_j \sim N(0, 0.05^2)$ is added to embed the $3\text{-}D$ Mobius into $p\text{-}D$, where $j = 4, \dots, p$.

>>>>

The Mobius strip is generated using `geozoo::mobius(n, p = 3)$points`, which samples $n$ points from a parameterization of the surface defined by angle $\theta$ and strip width $w$. The cartesian coordinates are $X_1 = \left(1 + w/2 \cos(\theta/2)\right) \cos(\theta)$, $X_2 = \left(1 + w/2 \cos(\theta/2)\right) \sin(\theta)$, and $X_3 = w/2 \sin(\theta/2)$. This maps a $2\text{-}D$ band with a half-twist into $3\text{-}D$ space, forming a non-orientable one-sided surface. For $p > 3$, Gaussian noise $X_j \sim N(0, 0.05^2)$ is added to embed the $3\text{-}D$ Mobius into $p\text{-}D$, where $j = 4, \dots, p$.
